### 2017-01-30 manuscript.rmd
typos

There has been considerable recent intrest in, and controversy about, the ortholog conjecture [@Koonin:2005fp; @Studer:2009bm; @Nehrt:2011bm; @Gabaldon:2013fi]. Our results are consistent with multiple studies that have not found support for the ortholog conjecture [@Studer:2009bm; @Nehrt:2011bm; @Yanai:2004hk]. Another sudy found only slightly greater similarity between orthologs than paralogs [@Altenhoff:2012ea].

Our reanalysis of KMRR using phylogenetic methods suggests that the ortholog conjectures is not a dominant pattern that is central to explaining the evolution of phenotypic diversity in gene families. This has important biological implications. It suggests that the mechanism of gene divergence (speciation versus duplication) may not have as strong an impact on phenotypic divergence as sometimes proposed. It also has technical implications. Rather than focus on whether genes are orthologs or paralogs when attempting to predict function, it may be more effective to simply focus on how closely related or distantly related they are. Closely related paralogs, for example, may tend to have more similar phenotypes than more distantly related orthologs [@Studer:2009bm].

The ortholog conjecture does not have to be an all or nothing question. It may be the case that the rates of phenotypic evolution following duplication may be greater than that following duplication in some organisms, gene families, and evolutionary processes. We just don't find evidence for it when summarizing gene expression acriss tissues with Tau in these mammals. This calls into question the general predictive power of the ortholog conjecture, and until these processes are better understood it will be necessary to test for it in each situation. These tests should be articulated in terms of clear alternative hypotheses [@Studer:2009bm] that make distinct phylogenetic comparative predictions.

>>>>

There has been considerable recent interest in, and controversy about, the ortholog conjecture [@Koonin:2005fp; @Studer:2009bm; @Nehrt:2011bm; @Gabaldon:2013fi]. Our results are consistent with multiple studies that have not found support for the ortholog conjecture [@Studer:2009bm; @Nehrt:2011bm; @Yanai:2004hk]. Another study found only slightly greater similarity between orthologs than paralogs [@Altenhoff:2012ea].

Our reanalysis of KMRR using phylogenetic methods suggests that the ortholog conjecture is not a dominant pattern that is central to explaining the evolution of phenotypic diversity in gene families. This has important biological implications. It suggests that the mechanism of gene divergence (speciation versus duplication) may not have as strong an impact on phenotypic divergence as sometimes proposed. It also has technical implications. Rather than focus on whether genes are orthologs or paralogs when attempting to predict function, it may be more effective to simply focus on how closely related or distantly related they are. Closely related paralogs, for example, may tend to have more similar phenotypes than more distantly related orthologs [@Studer:2009bm].

The ortholog conjecture does not have to be an all or nothing question. It may be the case that the rates of phenotypic evolution following duplication may be greater than that following duplication in some organisms, gene families, and evolutionary processes. We just don't find evidence for it when summarizing gene expression across tissues with Tau in these mammals. This calls into question the general predictive power of the ortholog conjecture, and until these processes are better understood it will be necessary to test for it in each situation. These tests should be articulated in terms of clear alternative hypotheses [@Studer:2009bm] that make distinct phylogenetic comparative predictions.
